\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-22 paper.20210121.tex

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30 $\times$ at the expense of only a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is only 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_d$& \multicolumn{6}{|l}{whether demand $d$ is admitted}\\
\hline
%$f_{d}^t$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_d^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $d$ over tunnel $t$}\\
\hline
$h_d$& \multicolumn{6}{|l}{profit (after refunding)  for demand $d$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_d^{\mathbf{z}}$&\multicolumn{6}{|l}{Whether scenario $\mathbf{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}

\section{$\mathsf{BATE}$ framework}\label{HATE}
In this section, we discuss the details of $\mathsf{BATE}$, which contains three parts, i.e., admission control, traffic scheduling and failure recovery, using notations summarized in Table \ref{Notation}. 
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High admission ratio and low admission latency:}  
  Bandwidth availability demands might arrive at anytime. 
  The system should be able to efficiently accommodate as many BA demands as possible under the constraint of network capacity and failure probabilities, as this would increase service agility and bring more revenue. %availability and bandwidth targets.
\item \textbf{High availability for allocated bandwidth:}
The system should be able to optimize its achieved availability in a probabilistic manner, 
as this would, in the long term, reduce potential penalties (i.e., refund due to SLA violations) and retain a good reputation. This can be achieved by making a good match between demands on higher availability and paths with lower failure probability.
%make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
%Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Automatic and economical failure recovery:}
If any link failure really happens, the system should reroute traffic away from that link, 
while minimizing any possible collateral damage to normal traffic, i.e., congestion and lower bandwidth availability due to contention from the rerouted traffic.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Abstraction of bandwidth availability}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer demanding Inter-DC WAN bandwidth resourses could be any application or tenant  spanning multiple DCs, in either a public or a private cloud. 
%a tenant of a public cloud (e.g., Amazon AWS), who uses this substrate to build his own virtual private cloud over multiple DCs, or could be a service team who launches multiple VM instances in a private cloud (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
%Currently, there is no interface for tenants to specify bandwidth availability.
Our abstraction of network failure scenarios and bandwidth availability demands in $\mathsf{BATE}$ are as follows.

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The Inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the DCs, 
and the set of links $V$ represent directed links between them. 
A network scenario $\mathbf{z}=\{mathbf{z}_1,mathbf{z}_2,...,mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($mathbf{z}_i=1$) or down ($mathbf{z}_i=0$), 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
and we also assume network operators can use historical data to estimate the failure probability $x_i$ for this link. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
Then, the expected probability that network scenario  $\mathbf{z}$ will happen \cite{Teavar} is given by 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i)(x_i))
\end{eqnarray}

\textbf{To be updated, follow Fig.1 )
For example, an inter-DC WAN contains three links $E=\{e_1,e_2,e_3\}$. 
Network scenario $\{1,1,0\}$ means $e_1$ ,$e_2$ are available and  $e_3$ fails.
If the up probability of $e_1,e_2,e_3$ are 0.9, 0.8, 0.85, respectively.
Then its probability $p(\{1,1,0\}) =0.9\times0.8\times0.15=0.108$.

\textbf{BA demand model:}
%We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the set of all source-destination (s-d) DC pairs.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
A bandwidth availability demand $d$ is in the form of $(\mathbf{b}_d, \beta_d)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, \mathbf{b}_d^2, ...>$ of bandwidth demands over all s-d pairs \footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Traffic engineering model:}
Our Traffic Engineering uses tunnel-based forwarding \cite{FFC,swan,Teavar}.%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
We use $D$ and $\hat{D}$ to represent arrived demands and \textit{admitted} demands, respectively.
Given a demand $d$, our traffic engineering scheme will decide whether to admit it (i.e., $g_d$), 
and the bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ over tunnel $t$ will be $f_d^t$.
Under the above network failure scenario model, we also use 
$v_t^{\mathbf{z}}$ to denote whether tunnel $t$ is available (i.e., $v_t^{\mathbf{z}}=1$)  or not  (i.e., $v_t^{\mathbf{z}}=0$) under the network scenario $\mathbf{z}$. 
Given an allocation result ${f_d^t | \foreach t \in T_k, k \in K}$, 
if (1) the total bandwidth allocated for each s-d pair $k$, i.e., $\sum_{\foreach t \in T_k} f_d^t}$, 
is equal to the bandwidth demand $\mathbf{b}_d^k$ for that pair, and 
(2) for every tunnel $t$ that is used in the allocation (i.e., $\f_d^t>0$), 
its expected availability under all possible network failure scenarios, 
i.e., $\sum_{\mathbf{z}} \in Z} p_{\mathbf{z}} \times v_t^{\mathbf{z}} $, 
is no less than the availability demand $\beta_d$, 
then we say this BA demand is satisfied by this exact allocation result in a probabilistic sense. 
If a failure indeed occurs, our traffic engineering scheme will try to reroute traffic that is affected by this failure. If any availability target is violated, a refund will be given back to the customer (see $\S$\ref{background}), and we use $h_d$ to denote the profit (after refunding) for demand $d$.

>>>>

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30 $\times$ at the expense of a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{When an admitted demand finishes, it will be removed from $D_a$.} }\\
\hline
\multirow{3}{*}{$d=(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{for a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_d$& \multicolumn{6}{|l}{whether demand $d$ is admitted}\\
\hline
%$f_{d}^t$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_d^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $d$ over tunnel $t$}\\
\hline
$h_d$& \multicolumn{6}{|l}{profit (after refunding)  for demand $d$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_d^{\bm{z}}$&\multicolumn{6}{|l}{Whether scenario $\bm{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}

\section{$\mathsf{BATE}$ framework}\label{HATE}
In this section, we discuss the details of $\mathsf{BATE}$, which contains three parts, i.e., admission control, traffic scheduling and failure recovery, using notations summarized in Table \ref{Notation}. 
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High admission ratio and low admission latency:}  
  Bandwidth availability demands might arrive at anytime. 
  The system should be able to efficiently accommodate as many BA demands as possible under the constraint of network capacity and failure probabilities, as this would increase service agility and bring more revenue. %availability and bandwidth targets.
\item \textbf{High availability for allocated bandwidth:}
The system should be able to optimize its achieved availability in a probabilistic manner, 
as this would, in the long term, reduce potential penalties (i.e., refund due to SLA violations) and retain a good reputation. This can be achieved by making a good match between demands on higher availability and paths with low failure probability.
%make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
%Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Automatic and economical failure recovery:}
If any link failure really happens, the system should reroute traffic away from that link, 
while minimizing any possible collateral damage to normal traffic, i.e., congestion and lower bandwidth availability due to rerouting.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Abstraction of bandwidth availability demands}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer could be a tenant who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify bandwidth availability.
We now present $\mathsf{BATE}$ 's availability abstraction.

\textbf{BA demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the a source and destination DC pair.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
For a  bandwidth availability demand $d$, the BA abstraction can be presented as $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, \mathbf{b}_d^2, ...>$ of bandwidth demands over all s-d pairs.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Network providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $h_d$ to denote the profit (after refunding) for demand $d$.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Network  model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
A network scenario $\bm{z}=\{z_1,z_2,...\}$ is a vector consisting of each link's state.
Each element $z_i \in \{0,1\}$ denotes whether link  $i$  is up ($z_i=1$) or down  ($z_i=0$).
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
The up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $\bm{Z}$ present the network scenario set and $p_{\bm{z}}$ is the probability of scenario $\bm{z}\in \bm{Z}$.
%Each link is up with the probability of $p_i$. \cite{Teavar}
Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
Similar to TEAVAR \cite{Teavar},  probability of network scenario  $\bm{z}$ is given by:

\begin{eqnarray} \label{state}
p_{\bm{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
&=&\prod_{i=1}^{|E|}(z_i'p_i+(1-z_i')(1-p_i))
\end{eqnarray}

For example, an inter-DC WAN contains three links $E=\{e_1,e_2,e_3\}$. 
Network scenario $\{1,1,0\}$ means $e_1$ ,$e_2$ are available and  $e_3$ fails.
If the up probability of $e_1,e_2,e_3$ are 0.9, 0.8, 0.85, respectively.
Then its probability $p(\{1,1,0\}) =0.9\times0.8\times0.15=0.108$.
